---
title: "Assignment4_Coffee"
output: html_document
date: "2023-10-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
ASSIGNMENT 4 COFFEE


```{r}
library(tidyverse)

df_C <- read.csv("Coffee_BP.csv")
view(df_C)

df_C %>% 
  ggplot(aes(CCoffee, BP))+
  geom_point()+
  geom_smooth(method="lm")

set.seed(1)
df_C$id <- 1:nrow(df_C)
train_C <- df_C %>%  sample_frac(0.80)
test_C1 <- anti_join(df_C, train_C, by="id")

model_C <- lm(BP ~ CCoffee, data=train_C)
summary(model_C)

test_C1$pred_BP <- predict(model_C, test_C1)
view(test_C1)

predict(model_C, data.frame(CCoffee=c(6, 8)))

```


```{r pressure, echo=FALSE}
df_C <- df_C %>% 
  add_row(BP = 148.14, CCoffee = 6)


df_C <- df_C %>% 
  add_row(BP = 152.21, CCoffee = 8)
view(df_C)

df_C %>% 
  ggplot(aes(CCoffee, BP))+
  geom_point()+
  geom_smooth(method="lm", color="yellow")


```
There is a positive relationship between number of cups of coffee consumed and blood pressure. 
This means the higher the number of cups of coffee consumed the higher the blood pressure.
The individual should reduce consumption of coffee, based on this dataset.

Also the Pvalue is close to zero at 0.04363,  (the P-value is the level of marginal significance within a statistical hypothesis test, representing the probability of the occurrence of a given event) shows that the probability of occurrence is high. 

